Supplement for: Carbon cycling in mature and regrowth forests globally: a macroecological synthesis based on the global Forest Carbon (ForC) database

### 2020-09-21 manuscript/ERL_global_C_review.Rmd
knit in filled version of table 1

ForC v.XX yielded a fairly comprehensive and internally consistent picture of C cycling in the world's major forest biomes. 
Carbon cycling rates generally increased from boreal to tropical regions and with stand age. 
Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. 6-7). 
In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 2-5, 7). 
The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 6-11). 
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks of mature forests are influenced by a different set of drivers.

>>>>

ForC v.XX yielded a fairly comprehensive and internally consistent picture of C cycling in the world's major forest biomes. 
Carbon cycling rates generally increased from boreal to tropical regions and with stand age. 
Specifically, the major C fluxes were highest in tropical forests, intermediate in temperate (broadleaf or conifer) forests, and lowest in boreal forests -- a pattern that generally held for regrowth as well as mature forests (Figs. 6-7). 
In contrast to C fluxes, there was little directional variation in mature forest C stocks across biomes (Figs. 2-5, 7). 
The majority of flux variables, together with most live biomass pools, increased significantly with stand age (Figs. 6-11). 
Together, these results indicate that, moving from cold to tropical climates and from young to old stands, there is a general acceleration of C cycling, whereas C stocks and $NEP$ of mature forests are influenced by a different set of drivers.
